The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-04-24 paper/ms.tex
caption

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{muhisto.eps}
\end{center}
\caption{Integrated flux distribution, $F(\mu)$, as a function of the
  viewing angle as parameterized by $\mu$. We show the results for the
  homogeneous source distribution in models with rotational velocities
  $0,100,200,300$\kms and  optical depths $10^5$, $10^6$, $10^7$. We
  see that the distribution is flat, meaning that the flux for all
  viewing angles is the same. The results for the central sources are
  similar. 
\label{fig:muhisto}}
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{muhisto.eps}
\end{center}
\caption{Integrated flux distribution, $F(\mu)$, as a function of the
  viewing angle as parameterized by $\mu$. We show the results for the
  homogeneous source distribution in models with rotational velocities
  $0$\kms, $300$\kms and  optical depths $10^5$, $10^6$ and $10^7$. We
  see that the distribution is flat, meaning that the flux for all
  viewing angles is the same. The results for the central sources are
  similar. 
\label{fig:muhisto}}
\end{figure}
